Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/related.tex
shorten configassure related work

\paragraph*{SDN Languages}
\sysname{} was heavily influenced by recent SDN programming
languages such as NetKAT~\cite{netkat}, Merlin~\cite{foster:merlin}, FatTire~\cite{fattire}, 
as well as path queries~\cite{queries}.
Each of these languages is oriented around regular expressions, which
describe paths through a network, and predicates, which classify packets.
In particular, FatTire allows programmers to define sets of paths together
with a fault tolerance level (\emph{i.e.,} tolerate 1 or 2 faults)
and the compiler will generate appropriate
OpenFlow rules.  \sysname is more
expressive as it allows users to specify preferences among
paths and it automatically generates distributed
implementations that tolerate
any number of faults.  Because FatTire generates data plane rules up front,
before faults occur, specifying higher levels of fault tolerance comes
at the cost of generating additional rules that tax switch
memory.  In contrast, \sysname uses traditional distributed
control plane mechanisms to react to faults, which do not impose
additional memory cost.
Because of the differences in the underlying technology, the analyses
and compilation algorithms used in \sysname are quite different from
previous work on SDN.  Finally, in addition to using path-based abstractions
for intra-domain routing, \sysname uses them for inter-domain routing as
well, unlike any existing SDN language.

\paragraph*{Configuration Synthesis}
ConfigAssure~\cite{narain:lisa05,narain+:configassure}
is another system designed to
help users define and debug low-level router
configurations.  Inputs to
ConfigAssure include a \emph{configuration database}, which contains a
collection of tuples over constants and configuration variables, and a
\emph{requirement}, which is a set of constraints.  For instance, the
tuple \texttt{hsrp(rexa,rA1,int(1),int(2))} states that interface
\texttt{rA1} on device \texttt{rexa} belongs to the HSRP group defined
by configuration variable \texttt{int(1)} with virtual IP address
defined by configuration variable \texttt{int(2)}.  The constraint
\texttt{hsrp\_subnet([rexa-rA1,rexb-rB1])} states that a database
contains tuples defining HSRP group identifiers and virtual IPs for
interfaces \texttt{rA1} and \texttt{rB1} on devices \texttt{rexa} and
\texttt{rexb}.  The authors use a combination of logic programming and
SAT solving to find concrete values for configuration variables such
as \texttt{int(1)}.  ConfigAssure handles
configuration for a wide range of protocols and many
different concerns.  In contrast, the scope of \sysname is much
narrower.  In return, \sysname offers compact, higher-level
abstractions customized for our domain, such as regular paths, as well
as domain-specific analyses customized to those abstractions, such as
our failure safety analysis.  The implementation technology is also
entirely different, as we define algorithms over automata and graphs
as opposed to using logic programming and SAT-based model-finding.

>>>>

\paragraph*{SDN Languages}
\sysname{} was heavily influenced by recent SDN programming
languages such as NetKAT~\cite{netkat}, Merlin~\cite{foster:merlin}, FatTire~\cite{fattire}, 
as well as path queries~\cite{queries}.
Each of these languages is oriented around regular expressions, which
describe paths through a network, and predicates, which classify packets.
In particular, FatTire allows programmers to define sets of paths together
with a fault tolerance level (\emph{i.e.,} tolerate 1 or 2 faults)
and the compiler will generate appropriate OpenFlow rules.
\sysname is more expressive as it allows users to specify preferences among
paths and it generates distributed implementations that tolerate any number of faults. 
Because FatTire generates data plane rules up front, 
specifying higher levels of fault tolerance comes
at the cost of generating additional rules that tax switch memory.  
In contrast, \sysname uses traditional distributed
control plane mechanisms to react to faults, which do not impose additional memory cost.
Because of the differences in the underlying technology, the analyses
and compilation algorithms used in \sysname are quite different from
previous work on SDN.  Finally, in addition to using path-based abstractions
for intra-domain routing, \sysname uses them for inter-domain routing as
well, unlike any existing SDN language.

\paragraph{}

\paragraph*{Configuration Synthesis}
ConfigAssure~\cite{narain:lisa05,narain+:configassure}
is another system designed to
help users define and debug low-level router
configurations.  Inputs to
ConfigAssure include a \emph{configuration database}, which contains a
collection of tuples over constants and configuration variables, and a
\emph{requirement}, which is a set of constraints.  
%For instance, the tuple \texttt{hsrp(rexa,rA1,int(1),int(2))} states that interface
%\texttt{rA1} on device \texttt{rexa} belongs to the HSRP group defined
%by configuration variable \texttt{int(1)} with virtual IP address
%defined by configuration variable \texttt{int(2)}.  The constraint
%\texttt{hsrp\_subnet([rexa-rA1,rexb-rB1])} states that a database
%contains tuples defining HSRP group identifiers and virtual IPs for
%interfaces \texttt{rA1} and \texttt{rB1} on devices \texttt{rexa} and
%\texttt{rexb}.  
The authors use a combination of logic programming and
SAT solving to find concrete values for configuration variables.
%such as \texttt{int(1)}.  
ConfigAssure handles configuration for a wide range of protocols and many
different concerns.  In contrast, the scope of \sysname is much
narrower.  In return, \sysname offers compact, higher-level
abstractions customized for our domain, such as regular paths, as well
as domain-specific analyses customized to those abstractions, such as
our failure safety analysis.  The implementation technology is also
entirely different, as we define algorithms over automata and graphs
as opposed to using logic programming and SAT-based model-finding.
